---
title: "Quiz 2"
author: "Jeremy T. Finke"
date: "September 10, 2015"
output: html_document
---



Question 1
In the slidify YAML text. Changing the framework from io2012 to shower does what?
Your Answer 		Score 	Explanation
It changes nothing. 			
It changes the html5 framework thus changing the style of the slides. 	Correct 	1.00 	
It changes whether the document is self contained or requires being connected to the internet. 			
It changes the ability to display mathjax javascript rendering. 			
Total 		1.00 / 1.00 	
Question 2
You wrote R code in a slidify document as follows

```{r}
fit <- lm(y ~ x1 + x2 + x3)
summary(fit)
```


If you want to hide the results of the summary statement (yet still have it run) what should you do?
Your Answer 		Score 	Explanation
Comment the command as below but also use a bang symbol after the comment, as in #! summary(fit) 			
Add a echo = FALSE option in the {r} call of the code chunk 			
Add a results = 'hide' option in the {r} call of the code chunk 	Correct 	1.00 	
Comment out the command # summary(fit) 			
Total 		1.00 / 1.00 	
Question 3
You wrote R code in a slidify document as follows

```{r}
fit <- lm(y ~ x1 + x2 + x3)
summary(fit)
```


If you want to display the results, but not the actual code, what should you do?
Your Answer 		Score 	Explanation
Comment the command, but use a bang symbol after the comment, as in #! summary(fit) 			
Add a echo = TRUE option in the {r} call of the code chunk 			
Add a echo = FALSE option in the {r} call of the code chunk 	Correct 	1.00 	
Comment out the command # summary(fit) 			
Total 		1.00 / 1.00 	
Question 4
R studio presentation tool does what?
Your Answer 		Score 	Explanation
Creates a power point presentation from a generalized markdown format having an extension Rpres. 			
Creates a presentation that can only be run from within Rstudio. 			
Creates HTML5 slides using a generalized markdown format having an extention Rpres and creates reproducible presentations by embedding and running the R code from within the presentation document. 	Correct 	1.00 	
Creates presentable R code from within presentations. However, it does not actually run the code. 			
Total 		1.00 / 1.00 	
Question 5
In Rstudio presenter, if you do not want the code to be evaluated, what option do you need to add to the {r} options?
Your Answer 		Score 	Explanation
echo = FALSE 			
results = 'hide' 			
eval = FALSE 	Correct 	1.00 	
run = FALSE 			
Total 		1.00 / 1.00 	
Question 6
When presenting data analysis to a broad audience, which of the following should be done?
Your Answer 		Score 	Explanation
Present results in the chronological order in which it was performed. 			
Do not include figure captions. 			
Show every analysis and method that was done. 			
Summarize the problem first. 	Correct 	1.00 	
Total 		1.00 / 1.00
